Notes on two photon scattering of the molecular state

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Gramma/spelling

The two kinds of ground state scattering measurements we have are atomic state PA rate
and molecular state scattering (using Raman transition).
Assuming the laser is clean and no other states are involved,
\begin{enumerate}
\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
  one frequency so the Raman process can only come back down to the same energy as
  the initial state, which is not in an continuum.
\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
  similarly, the only energy the molecular state could couple to is the initial energy
  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
  The atomic state can indeed be coupled to the continuum but it should be much weaker than
  the molecular state (the up leg is much smaller) and we have not measured a decrease in
  atomic 2-body lifetime when the Raman beam is turned on.
\end{enumerate}
Therefore, in order to generate any loss from this process for the ground state,
we need to have either,
\begin{enumerate}
\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
  can couple the state of interest to the motional continuum. Or,
\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
  can couple to.\\
  Candidate for this continuum includes the center of mass (COM) motional states and
  the motional continuum from other HF states.\\
  The COM motional continuum actually also starts at a positive energy so it doesn't seems
  possible. The continuum from other HF states is much more promising especially since
  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
  the HF state with the lowest energy.
\end{enumerate}

@@

We can then consider a small enough volume around the $r=0$ of the relative coordinate.
The coupling to the excited molecular state is entirely determined by the wavefunction
inside. The wavefunction inside is determined by the boundary condition,
which for $L=0$\footnote{Or for any particular $L$ and $m_L$} is a single number,
and the energy of the state. Since the energy of the motional state is much smaller than
the depth of the interaction potential, we can expect the shape of the wavefunction
to be almost independent of the energy and the amplitude of it to be proportional to
the boundary condition. In the weak interaction limit\footnote{This should be true for most
  motional state with the exception of $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state.},
we can assume that the boundary condition is given by the value of
the non-interacting wavefunctions at $r=0$.\\

@@

After doing the subsitution of $u=r\psi_r(r)$, the Schr\"odinger equation for $u$ becomes
that of a 1D harmonic oscillator with a hard wall at $r=0$. The eigenstates are the odd
harmonic oscillator states for the normal 1D potential and $\psi(r=0)$ is given by $\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}$.\\

>>>>

The two kinds of ground state scattering measurements we have are atomic state PA rate
and molecular state scattering (using Raman transition).
Assuming the laser is clean and no other states are involved,
\begin{enumerate}
\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
  one frequency so the Raman process can only come back down to the same energy as
  the initial state, which is not in an continuum.
\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
  similarly, the only energy the molecular state could couple to is the initial energy
  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
  The atomic state can indeed be coupled to the continuum but it should be much weaker than
  the molecular state (the up leg is much smaller) and we have not measured a decrease in
  atomic 2-body lifetime when the Raman beam is turned on.
\end{enumerate}
Therefore, in order to generate any loss from this process for the ground state,
we need to have either,
\begin{enumerate}
\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
  can couple the state of interest to the motional continuum. Or,
\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
  can couple to.\\
  Candidate for this continuum includes the center of mass (COM) motional states and
  the motional continuum from other HF states.\\
  The COM motional continuum actually also starts at a positive energy so it doesn't seem
  possible. The continuum from other HF states is much more promising especially since
  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
  the HF state with the lowest energy.
\end{enumerate}

@@

We can then consider a small enough volume around the $r=0$ of the relative coordinate.
The coupling to the excited molecular state is entirely determined by the wavefunction
inside. The wavefunction inside is determined by the boundary condition,
which for $L=0$\footnote{Or for any particular $L$ and $m_L$} is a single number,
and the energy of the state. Since the energy of the motional state is much smaller than
the depth of the interaction potential, we can expect the shape of the wavefunction
to be almost independent of the energy and the amplitude of it to be proportional to
the boundary condition. In the weak interaction limit\footnote{This should be true for most
  motional state with the exception of $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state.},
we can assume that the boundary condition is given by the value of
the non-interacting wavefunction at $r=0$.\\

@@

After doing the substitution of $u=r\psi_r(r)$, the Schr\"odinger equation for $u$ becomes
that of a 1D harmonic oscillator with a hard wall at $r=0$. The eigenstates are the odd
harmonic oscillator states for the normal 1D potential and $\psi(r=0)$ is given by $\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}$.\\
